Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-01-21 text/src/article.tex
Write first section in results

% }}}
% {{{ Background
\section*{Background}
 Text for this section.\cite{koon,oreg,khar,zvai,xjon,schn,pond,smith,marg,hunn,advi,koha,mouse}
% }}}
% {{{ Implementation
%%%%%%%%%%%%%%%%%%%%%%
\section*{Implementation}
  Text for this section \ldots
% }}}
\section*{Results and Discussion} %{{{1
\subsection*{Scaffolder Description} %{{{2

  * Join contigs together
  * Add inserts
  * Add unknown gap regions
  * Specified in a YAML file format

\subsection*{Scaffold file format} %{{{2

>>>>

% }}}
% {{{ Background
\section*{Background}
 Text for this section.\cite{koon,oreg,khar,zvai,xjon,schn,pond,smith,marg,hunn,advi,koha,mouse}
% }}}
% {{{ Implementation
%%%%%%%%%%%%%%%%%%%%%%
\section*{Implementation}
  Text for this section \ldots
% }}}
\section*{Results and Discussion} %{{{1

\subsection*{Scaffolder Description} %{{{2

Scaffolder is a tool aimed at build genome sequence scaffolds through simple to
edit configuration files. Scaffolder allows contigs to be joined together
through defintition in the scaffold file. Each contigs is stored in a fasta
file, as provided by the standard output from an assembler such as
newbler\cite{newbler} or abyss\cite{abyss}. Scaffolder allows inserts to be
added to scaffold so that gaps in the assembled data may be bridged and filled
- a common process in finishing a genome sequence. Scaffolder also allows the
specification of unknown regions in the scaffold. These may be regions where
the sequence is unknown but the approximate size can be estimated from the
sequencing of insert pairs or from estimating distances from contigs aligned to
reference genomes.

Scaffolder provides a ruby API that allows the scaffold and designated
sequences to be manipulated through a ruby programme. This allows scaffolder to
be integrated into exiting genomics works flows such as using Rake. Scaffolder
all provides a command line binary for the manipulation of the scaffold. This
binary behaves as a standard unix command line interface returning appropriate
exit statuses and providing manual pages for each of the commands.

\subsection*{Defining a scaffold in a text file} %{{{2

The genome scaffold is defined YAML format. YAML is an easy to edit data format
that is both machine readable and easy to edit manually.

INSERT FIGURE WITH EXAMPLE LAYOUT OF SCAFFOLD
